---
title: "Week 9 project"
author: "Khue Tran"
date: "3/23/2020"
output: pdf_document
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output/")
  })

---


# Libraries
```{r, include=F}
library(tidyverse)
library(ggplot2)
library(psych)
```


# Data import

Data cleaning steps

* Change format of timeStart and timeEnd to date format

* Recode Condition as Block A, Block B, and Control

* Recode Gender as Male and Female

* Filter Q6 for attentive response 

```{r, warning=F, message=F}
week9_tbl <- read_csv("../data/week3.csv") %>%
  mutate(timeStart = lubridate::ymd_hms(timeStart), 
         timeEnd   = lubridate::ymd_hms(timeEnd)) %>% 
  mutate(condition = recode_factor(condition, "A" = "Block A", "B" = "Block B", "C" = "Control"),
         gender    = recode_factor(gender, "M" = "Male", "F" = "Female")) %>% 
  filter(q6 == 1)
```

# Visualization
```{r, echo=F}
week9_tbl <- week9_tbl %>%
  mutate(mean_Q1_Q5  = rowMeans(select(., q1:q5)),
         mean_Q6_Q10 = rowMeans(select(., q6:q10))) 

week9_tbl %>% 
  ggplot(aes(x = mean_Q1_Q5, y = mean_Q6_Q10)) +
  geom_point() + 
  geom_smooth(method = lm, se = F)
```


The scatter plot displays the relationship between mean of Q1 to Q5 and mean of Q6 to Q10.


# Analysis
```{r}
cor.test(week9_tbl$mean_Q1_Q5, week9_tbl$mean_Q6_Q10)
```

The correlation was -0.100891 (p>.05), which is not statistically significant.

# R shiny app

https://trann003.shinyapps.io/week9/